Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-12-13 Final Draft/Final Draft.Rmd
table 3 change

rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"

rownames(regResultList$secondStageModelWNetCA$coefficients 
)[rownames(regResultList$secondStageModelWNetCA$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC$coefficients
)[rownames(regResultList$secondStageModelWNetC$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"

rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelOurs_2$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelOurs_3$fitted.values"] <-  "Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelOurs_5$fitted.values"] <-  "White Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelOurs_6$fitted.values"] <-  "White Manufacturing Layoffs"

rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"
rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Manufacturing Layoffs"

names(regResultList$rseNetCA_2)[1] <- "Manufacturing Layoffs"
names(regResultList$rseNetC_2)[1] <- "Manufacturing Layoffs"
names(regResultList$rseWNetCA_2)[1] <- "White Manufacturing Layoffs"
names(regResultList$rseWNetC_2)[1] <- "White Manufacturing Layoffs"

names(regResultList$rseWNetCA_2)[names(regResultList$rseWNetCA_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"
names(regResultList$rseWNetC_2)[names(regResultList$rseWNetC_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Manufacturing Layoffs"

stargazer(regResultList$secondStageModelNetCA,
          regResultList$secondStageModelNetC,
          regResultList$secondStageModelWNetCA,
          regResultList$secondStageModelWNetC,
          se = list(
            regResultList$rseNetCA_2,
            regResultList$rseNetC_2,
            regResultList$rseWNetCA_2,
            regResultList$rseWNetC_2
          ),
          title = "Effect of Manufacturing Job Loss from 2004 to 2015",
          dep.var.labels = "Change in Dem. Share, 2016-2012",
          omit.stat = c("rsq","ser"),
          keep = c("Manufacturing Layoffs", "White Manufacturing Layoffs", "Nonwhite Manufacturing Layoffs"),
          add.lines = list(
            c("White Share/Svc Layoffs Control", "No", "Yes", "No", "Yes")
          ),
          digits = 2,
          header = F,
          type = "latex",
          label = "regResult12"
)

>>>>

rownames(regResultList$secondStageModelNetCA$coefficients )[rownames(regResultList$secondStageModelNetCA$coefficients)=="firstStageModelOurs_2$fitted.values"] <-  "Job Losses"
rownames(regResultList$secondStageModelNetC$coefficients )[rownames(regResultList$secondStageModelNetC$coefficients)=="firstStageModelOurs_3$fitted.values"] <-  "Job Losses"
rownames(regResultList$secondStageModelWNetCA$coefficients )[rownames(regResultList$secondStageModelWNetCA$coefficients)=="firstStageModelOurs_5$fitted.values"] <-  "White Job Losses"
rownames(regResultList$secondStageModelWNetC$coefficients )[rownames(regResultList$secondStageModelWNetC$coefficients)=="firstStageModelOurs_6$fitted.values"] <-  "White Job Losses"

rownames(regResultList$secondStageModelWNetCA$coefficients 
)[rownames(regResultList$secondStageModelWNetCA$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
rownames(regResultList$secondStageModelWNetC$coefficients
)[rownames(regResultList$secondStageModelWNetC$coefficients)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"

rownames(regResultList$secondStageModelNetCA$beta )[rownames(regResultList$secondStageModelNetCA$beta) =="firstStageModelOurs_2$fitted.values"] <-  "Job Losses"
rownames(regResultList$secondStageModelNetC$beta )[rownames(regResultList$secondStageModelNetC$beta)=="firstStageModelOurs_3$fitted.values"] <-  "Job Losses"
rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="firstStageModelOurs_5$fitted.values"] <-  "White Job Losses"
rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="firstStageModelOurs_6$fitted.values"] <-  "White Job Losses"

rownames(regResultList$secondStageModelWNetCA$beta )[rownames(regResultList$secondStageModelWNetCA$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"
rownames(regResultList$secondStageModelWNetC$beta )[rownames(regResultList$secondStageModelWNetC$beta)=="mfgNetChange_nonwhite"] <-  "Nonwhite Job Losses"

names(regResultList$rseNetCA_2)[1] <- "Job Losses"
names(regResultList$rseNetC_2)[1] <- "Job Losses"
names(regResultList$rseWNetCA_2)[1] <- "White Job Losses"
names(regResultList$rseWNetC_2)[1] <- "White Job Losses"

names(regResultList$rseWNetCA_2)[names(regResultList$rseWNetCA_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Job Losses"
names(regResultList$rseWNetC_2)[names(regResultList$rseWNetC_2) == "mfgNetChange_nonwhite"] <- "Nonwhite Job Losses"

stargazer(regResultList$secondStageModelNetCA,
          regResultList$secondStageModelNetC,
          regResultList$secondStageModelWNetCA,
          regResultList$secondStageModelWNetC,
          se = list(
            regResultList$rseNetCA_2,
            regResultList$rseNetC_2,
            regResultList$rseWNetCA_2,
            regResultList$rseWNetC_2
          ),
          title = "Effect of Manufacturing Job Loss from 2004 to 2015",
          dep.var.labels = "Change in Dem. Share, 2016-2012",
          omit.stat = c("rsq","ser"),
          keep = c("Job Losses", "White Job Losses", "Nonwhite Job Losses"),
          add.lines = list(
            c("White Share/Svc Layoffs Control", "No", "Yes", "No", "Yes")
          ),
          digits = 2,
          header = F,
          type = "latex",
          label = "regResult12"
)
